---
title: "AN588-Week-2"
author: "Sylvie Adams"
format: html
editor: visual
theme: "lux"
toc: true
toc-depth: 5
code-block-bg: true
code-block-border-left: "blue"
highlight-style: "gruvbox"
---

```{r}
library(tidyverse) # includes stringr
```

## Challenge 1

```{r}
# input text and split
Ulysses_string = "Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed."

Ulysses_vector <- gsub("[[:punct:]]","", Ulysses_string) # make vector of string w/o punctuation

Ulysses_vector_split <- str_split(Ulysses_vector, " ")[[1]] #split text and "unlist" Ulysses_vector_split

Ulysses_vector_split[seq(from = 1, to = length(Ulysses_vector_split), by = 3)] # take every third element
```

## Challenge 2

```{r}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE) # define matrix m

x <- m[, c(2, 3, 6)] # select columns 2, 3, and 6 of matrix m for x
x # print x

x <- m[6:8,] # select rows 6-8 of matrix m for x
x # print x

x <- m[2:6, 2:9] # select elements from row 2, column 2 to row 6, column 9 of matrix m for x
x # print x
```

## Challenge 3

```{r}
a <- array(data = 400:1, dim = c(5, 5, 4, 4)) # create array a (4 levels, 400 elements)
a # print array a

a[1, 1, 1, 2] # print first subset of a

a[2, 3, 2, ] # print second subset of a

a[1:5, 1:5, 3, 3] # print third subset of a
```

## Challenge 4

```{r}
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae") # Lemuroidea vector
Lorisoidea <- c("Lorisidae", "Galagidae") # Lorisoidea vector
Strepsirhini <- list(Lemuroidea, Lorisoidea) # Strepsirhini list
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea") # Name list elements

Catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae") #Catarrhini vector
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae") #Platyrrhini vector
Anthropoidea <- list(Catarrhini, Platyrrhini) #Anthropoidea list
names(Anthropoidea) <- list("Catarrhini", "Platyrrhini") # Name list elements

Tarsioidea <- c("Tarsioidea") # Tarsioidea vector
Haplorhini <- list(Tarsioidea, Anthropoidea) # Haplorhini list
names(Haplorhini) <- list("Tarsioidea", "Anthropoidea") # Name list elements

Primates <- list(Strepsirhini, Haplorhini) # Primates list
names(Primates) <- list("Strepsirhini", "Haplorhini") # Name list elements
Primates # Print primate taxonomy
```

## Challenge 5

```{r}
m3 = matrix(data = c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow = 5, ncol = 3, byrow = TRUE) # create matrix m3, stored by rows
m3 # Print matrix m3

m3_df <- as.data.frame(m3) # Coerce matrix m3 to data frame
m3_df # Print data frame m3

m3_df[, 2] <- as.logical(m3_df[, 2]) # Coerce second column of data frame to logical-valued
m3_df[, 2] # Print logical-valued column of m3_df

m3_df[, 3] <- as.factor(m3_df[, 3]) # Coerce third column of data frame to factor-valued
m3_df[, 3] # Print factor_valued column of m3_df

str(m3_df) # Show data type for each variable in data frame
```

## CHALLENGES

I struggled with the following things while writing my code:

1) Understanding how how to "unlist" an item line 26 of Challenge 1, or if I did it in the right way.

2) In Challenge 4 I wasn't sure always when to make a vector or list. I also didn't know if the structure or order I did it in was the best.

3) I'm not sure when to write install.packages() versus library() when I want a package to be installed as a part of my code.

4) I didn't know the best way to change particular features of my theme - I hope it ended up looking okay.

5) I struggled with pushing and uploading things between the remote and local repositories - I think if this is being read now then it turned out okay!